### 2016-11-28 Detector/Detector.tex
Some rephrasing

The \ac{LHC} does not operate on its own, a chain of accelerators leads
the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
of the \ac{CERN} accelerator complex.
\begin{figure}[h!]
\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
\label{fig:lhc_schematic}
\end{figure}
Protons originate from hydrogen gas, where electrons are stripped off the 
hydrogen atoms using an electric field. The protons then pass through an injector
chain which increases the energy of the protons in several steps. After the protons
are created from the hydrogen gas, they are accelerated to an energy of
50 MeV in the Linac2 linear accelerator. They are then passed on to the
\acf{PSB} which accelerates the protons until they reach an energy of 1.4 GeV.
The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
reached the protons are injected into the \ac{LHC} in two counter-rotating
beams. In the \ac{LHC} ring the beams are further accelerated to the required centre of mass energy
by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
of $\mathcal{O}(10^{11})$ protons, spaced 25ns apart. The beams are kept in circulation
using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
a temperature of 1.9K and generating magnetic fields upwards of 8 T.
The beams collide at four points
around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
CMS%\cite{cms-jinst} guess we've cited this already
, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.

@@

The tracker provides coverage up to $|\eta| < 2.5$ and consists of
several different components. A schematic of the tracking detector is given
in figure \ref{fig:CMS_tracker}. The part of the tracking system
closest to the interaction point is the silicon pixel detector, which 
consists of 3 layers of pixels in the barrel of the detector, with 
2 pixel endcap disks. The barrel layers sit at radii of 4.4, 7.3 and 10.2 cm 
and extend up to $z=\pm 26.5$ cm, with the disks placed at $z=\pm 34.5$ cm and
$z=\pm 46.5$ cm. The pixel detector consists of 66 million silicon pixels, each
$100 \mu m \times 150 \mu m$ in size. The choice of this pixel size is driven
by the achievable spatial resolution, which is $15-20 \mu m$ in the $r$ and $z$ directions.
This allows for 3D vertex reconstruction. With this layout, the pixel tracker
provides 3 precise position measurements along each charged particle trajectory.

@@

Beyond the pixel detector the tracking system is made up of a silicon
strip detector consisting of multiple different subsystems. The first part of the
silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing 4 layers of
silicon strip detectors in the barrel plus 3 disks at both ends. These two systems
extend out towards a radius of 55 cm. The barrel layers and disks each consist
of silicon strips which are 10 cm long, $80-141~\mu$m wide and $320~\mu$m thick. The \ac{TIB} and \ac{TID}
provide 4 measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu m$.
The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of 6 layers of silicon strip sensors extending
up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500~$\mu$m thick, around 25 cm long and 122-183 $\mu$m 
wide and this subdetector provides 6 measurements of $r$ and $\phi$, with a resolution
of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
consisting of 9 disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
This part of the system provides up to 9 $\phi$ measurements.

@@

The pixel tracker will be upgraded during the extended year-end technical stop in early 2017 \cite{cms-pixel-upgrade}. %or just replaced?

@@

Despite being further away from the interaction
point than the tracker, the materials in other parts of the detector
still need to be radiation hard. In order to be able to place
the calorimeters inside the bore of the solenoid, a compact \ac{ECAL}
had to be constructed, and to provide excellent resolution a 
highly granular system had to be designed. The lead tungstate crystals have a 
radiation length of 0.89 cm, a Moli\`ere radius of 2.2 cm, and 80\% of the light
from the crystals is emitted in 25 ns. This short radiation
length, small Moli\`ere radius and short scintillation decay time combined
with the radiation hardness of the material motivate the choice of lead tungstate.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the geometry. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
Each endcap is divided into two halves. In front of the endcaps 
the preshower detectors, covering $1.653<|\eta|<2.6$ are sampling
calorimeters whose main use is to indentify neutral pions in the endcaps. Additionally
they help electron identification and improve the resolution
of position determination. Each of the two preshower detectors consist
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower comprises 3 radiation lenghts.

@@

\subsection{\acl{HCAL}}
\label{sec:CMSLHC_CMS_hcal}
The \ac{ECAL} is surrounded by the \ac{HCAL}, which is important for the
measurement of the energies of strongly interacting particles. As
the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
starts at a radius of 2.95 m, space for the \ac{HCAL} inside the magnet
coil is limited. Therefore the barrel region of the \ac{HCAL} consists
of the \ac{HB}, which sits inside the magnet coil, and the \ac{HO}, sitting outside it, 
to complement the \ac{HB}. The \ac{HB} and \ac{HO}  provide coverage up to $|\eta|<1.3$, 
beyond which they are complemented by the \ac{HE} and the \ac{HF}. The \ac{HE} provides
coverage between $1.3<|\eta|<3$ with the \ac{HF} extending this coverage up to $|\eta| = 5.2$
The locations of the different subcomponents of the \ac{HCAL} are shown
in figure \ref{fig:CMS_HCAL}.

@@

The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The brass used as 
absorber fits the constraints imposed by the environment due to its short interaction length
of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range. 
The light from each tile is collected with a wavelength-shifting fibre, 
which is read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
sufficient to identify for example late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lenghts. 
Like in the \ac{HB} the active material consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
to a hybrid photodiode via wavelength shifting fibres.
%WTF: wavelength-shifting fibres

@@

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}
One of the main physics goals of the \ac{CMS} experiment
at design was to search for $H\rightarrow ZZ\rightarrow 4\mu$ decays. Muons
suffer less from radiative losses in the tracker material, which means the most accurate
4-body mass can be constructed when using the dimuon final state of the $Z$'s.
Since the discovery of the Higgs boson the ZZ channel has continued to be an important
final state for Higgs measurements, at the same time many \ac{BSM} searches also make use of 
signatures with muons in the final state.
All of this means that good muon identification efficiency and precise muon momentum resolution
are very important. The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
are all necessary to ensure the identification requirements can be met. It is located
outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
regions as both \ac{DT} and \ac{CSCs}, is used as a dedicated triggering system.

>>>>

The \ac{LHC} does not operate on its own, a chain of accelerators leads
the protons into the \ac{LHC}. Figure \ref{fig:lhc_schematic} shows a schematic
of the \ac{CERN} accelerator complex.
\begin{figure}[h!]
\includegraphics[width=0.8\textwidth]{./Detector/Plots/LHC_default.jpg}
\caption{Schematic of the \ac{CERN} accelerator complex \cite{lhc-schematic}.}
\label{fig:lhc_schematic}
\end{figure}
Protons originate from hydrogen gas, where electrons are stripped off the 
hydrogen atoms using an electric field. The protons then pass through an injector
chain which increases the energy of the protons in several steps. After the protons
are created from the hydrogen gas, they are accelerated to an energy of
50 MeV in the Linac2 linear accelerator. They are then passed on to the
\acf{PSB} which accelerates the protons until they reach an energy of 1.4 GeV.
The next accelerator in the chain, the \acf{PS}, further accelerates the protons to 25 GeV,
with the \acf{SPS} bringing the energy up to 450 GeV. When this energy has been 
reached the protons are injected into the \ac{LHC} in two counter-rotating
beams. In the \ac{LHC} ring the beams are further accelerated to the required centre of mass energy
by eight \ac{RF} cavities. At design operation the beams consist of 2808 proton bunches each made up 
of $\mathcal{O}(10^{11})$ protons, spaced 25ns apart. The beams are kept in circulation
using 1232 niobium-titanium superconducting dipole magnets, cooled to operate at 
a temperature of 1.9K and generating magnetic fields upwards of 8 Tesla.
The beams collide at four points
around the \ac{LHC} ring, where the collisions are recorded by the ATLAS\cite{atlas-jinst}, 
CMS%\cite{cms-jinst} guess we've cited this already
, ALICE\cite{alice-jinst}, and LHCb\cite{lhcb-jinst} detectors.

@@

The tracker, providing coverage up to $|\eta|<2.5$ consists of 
several different components. A schematic of the tracking detector, indicating
the location of these components, is given in figure \ref{fig:CMS_tracker}.
Nearest the interaction point the tracker is a pixel detector made
of 66 million silicon pixels, each 100 $\mu$m $\times$ 150 $\mu$m in size.
The choice of this pixel size is driven by the achievable spatial resolution,
which is 15-20 $\mu$m in the $r$ and $z$ directions in this case. Such a
precise resolution allows for 3D vertex reconstruction. The pixel
detector consists of 3 layers of pixels in the barrel region, with 2 pixel disks 
placed in the endcap region at either side. The barrel layers sit at radii of
4.4, 7.3 and 10.2 cm and extend out up to $z=\pm 26.5$ cm. The disks are placed
at $z=\pm 34.5$ cm and $z=\pm 46.5$ cm. With this layout the pixel tracker can
provide three precies position measurements along each charged particle trajectory.

@@

Beyond the pixel detector the tracking system is made up of a silicon
strip detector consisting of multiple different subsystems. The first part of the
silicon strip tracker consists of the \ac{TIB} and \ac{TID}, providing four layers of
silicon strip detectors in the barrel plus three disks at both ends. These two systems
extend out towards a radius of 55 cm. The barrel layers and disks each consist
of silicon strips which are 10 cm long, $80-141~\mu$m wide and $320~\mu$m thick. The \ac{TIB} and \ac{TID}
provide four measurements of the $r-\phi$ position  with a resolution of 23-35 $\mu$m.
The \ac{TIB} and \ac{TID} are surrounded by the \ac{TOB}, which consists of six layers of silicon strip sensors extending
up to an outer radius of 116 cm and up to $z=\pm 118$ cm. The strips in the \ac{TOB} are 500~$\mu$m thick, around 25 cm long and 122-183 $\mu$m 
wide and this subdetector provides 6 measurements of $r$ and $\phi$, with a resolution
of 35-53 $\mu$m. Beyond the z-range covered by the \ac{TOB}, coverage is provided by the \ac{TEC},
consisting of nine disks of strips. In the \ac{TEC}, the strip thickness ranges from 320-500 $\mu$m and the the strip width ranges from $97-184 \mu m$.
This part of the system provides up to nine $\phi$ measurements.

@@

The pixel tracker will be upgraded during the extended year-end technical stop in early 2017. This upgrade is needed to
maintain the performance of the tracker as the pile-up increases \cite{cms-pixel-upgrade}. %or just replaced?

@@

The choice of lead tungstate crystals is motivated by the
radiation-hardness of the material in combination with its
short radiation length, small Moli\`ere radius and short scintillation
decay time. With a radiation length of 0.89 cm and a Moli\`ere radius of 2.2 cm,
lead tungstate crystals allow for the construction of a compact, highly 
granular \ac{ECAL}. The compactness of the \ac{ECAL} is required in 
order to be able to fit the calorimeters inside the bore of the magnet. 
As 80\% of the light from the crystals is emitted within 25 ns, that is
within the time between two bunch crossings at design operation of the \ac{LHC},
the lead tungstate crystals satisfy the requirements imposed by the \ac{LHC} operating
parameters.

@@

Figure \ref{fig:CMS_ECAL} shows a schematic of the \ac{ECAL}, indicating
the subsystems it is made up of. The \ac{ECAL} consists of different subsystems. The \ac{EB} 
covers the pseudorapidity range up to $|\eta|<1.479$, with
crystals of $0.0174 \times 0.0174$ in $\eta - \phi$. The \ac{EE}
provides coverage beyond the range of the \ac{EB}, up to $|\eta|<3.0$
Each endcap is divided into two halves. In front of the endcaps 
the preshower detectors, covering $1.653<|\eta|<2.6$ are sampling
calorimeters whose main use is to indentify neutral pions in the endcaps. Additionally
they help electron identification and improve the resolution
of position determination. Each of the two preshower detectors consist
of two layers of lead radiators to initiate the shower, with silicon sensors
placed after each layer of radiators to measure the deposited energy. The 
total thickness of the preshower comprises 3 radiation lenghts.

@@

\subsection{\acl{HCAL}}
\label{sec:CMSLHC_CMS_hcal}
The \ac{ECAL} is surrounded by the \ac{HCAL}, which is important for the
measurement of the energies of strongly interacting particles. As
the \ac{ECAL} extends out to a radius of 1.77 m and the magnet coil
starts at a radius of 2.95 m, space for the \ac{HCAL} inside the magnet
coil is limited. The \ac{HCAL} design takes
this into account by placing part of the subdetector outside the magnet coil. A schematic of the
\ac{HCAL}, indicating the different components of the \ac{HCAL} is shown
in figure \ref{fig:CMS_HCAL}.

@@

In the barrel region the \ac{HB}, limited in radius by the magnet coil, provides
coverage up to $|\eta|<1.3$. Beyond this $\eta$ range the \ac{HE} covers
the region up to $|\eta|<3$. The \ac{HB} and \ac{HE} are sampling calorimeters made of brass absorber
plates with tiles of plastic scintillator as the active material. The brass used as 
absorber fits the constraints imposed by the environment due to its short interaction length
of 16.42 cm and the fact that it is non-magnetic. The tiles of scintillator 
are $0.087 \times 0.087$ in $\eta-\phi$ for $|\eta|<1.6$ and $0.17\times0.17$ in $\eta-\phi$
beyond this range. 
The light from each tile is collected with a wavelength-shifting fibre, 
which is read out using a hybrid photodiode. In the barrel, the \ac{HCAL}
has a thickness of between 5.82 and 10.6 interaction lenghts, which is not 
sufficient to identify for example late-starting showers. The \ac{HO}, sitting
outside of the magnet and using the coil as an additional absorber, extends the 
thickness to at least 11.8 interaction lenghts. 
Like in the \ac{HB} the active material of the \ac{HO} consists of plastic scintillator tiles which roughly
map the granularity of the tiles in the \ac{HB}, and are read out by feeding the light
to a hybrid photodiode via wavelength shifting fibres.
%WTF: wavelength-shifting fibres

@@

\subsection{Muon system}
\label{sec:CMSLHC_CMS_muons}
Precise muon identification is one of the requirements of the \ac{CMS} 
experiment. Good muon identification efficiency and precision muon momentum 
resolution are very important, as muons appear as final states in many
\ac{BSM} signatures the experiment is used to search for. In addition to
that, final states with muons are very important for the detection of $H\rightarrow ZZ \rightarrow 4\ell$ decays.

The \ac{CMS} muon system \cite{cms-jinst} is made up out of three different subsystems which
are all necessary to ensure the identification requirements can be met. It is located
outside of the magnet coil, interspersed in the iron return yoke of the solenoid.
In the barrel of the detector the \ac{DT} chambers provide coverage for $|\eta|<1.2$, with
the \ac{CSCs} covering the $0.9<|\eta|<2.4$ region. The \ac{RPCs}, covering the same
regions as both \ac{DT} and \ac{CSCs}, is used as a dedicated triggering system.
